DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-05 paper/appendix.tex
Update control loop graph
Also changed location of training loss graph
Add (unlikely) graph of network
The graph ended up being very large. The one currently being used will
have to be changed since it is very hard to see.

\subsection{DNN Training and Testing}
We train a neural network model across a set of 30 completed runs on 
the track seen in Figure~\ref{fig:track} by a human pilot. Half of 
the runs saw the car driving one way along the track, while the 
remaining half were of the car driving in the opposite direction on 
the track. In total, we collected 2,556 frames for training and 2,609 
frames for validation. In each training step, we use a batch size of 
100 frames which are used to further develop the model. We do this 
across 2,000 training steps. When a model was trained with the 
aformentioned data, the training loss was 0.0188 and the validation 
loss was 0.0132.

\begin{figure}[t]
  \centering
  \includegraphics[width=.55\textwidth]{figs/TrainingLoss}
  \caption{DeepPicar's control loop processing times over 1000 input 
image frames.}
  \label{fig:modelloss}
\end{figure}

We also trained models where center frames (where the car was going 
straight) and curve frames (where the car was turning) were equally 
selected in each batch, and were pleasantly surprised at the change 
in the car's performance. With the second model, the car displayed a 
greater ability to stay in the center of the track (on the white 
tape). This was problematic, however, as the loss values changed with 
the training loss being 0.009 and the validation loss becoming 
0.0869, indicating that overfitting had become a problem. We believe, 
though, that this can be rectified through the collection of 
additional data for training and validation.

>>>>

\subsection{DNN Training and Testing}
We train a neural network model across a set of 30 completed runs on 
the track seen in Figure~\ref{fig:track} by a human pilot. Half of 
the runs saw the car driving one way along the track, while the 
remaining half were of the car driving in the opposite direction on 
the track. In total, we collected 2,556 frames for training and 2,609 
frames for validation. In each training step, we use a batch size of 
100 frames which are used to further develop the model. We do this 
across 2,000 training steps. When a model was trained with the 
aformentioned data, the training loss was 0.0188 and the validation 
loss was 0.0132. The change of the loss value over the course of model training can be seen in Figure~\ref{fig:modelloss}.

\begin{figure}[h]
  \centering
  \includegraphics[width=.55\textwidth]{figs/TrainingLoss}
  \caption{Change in loss value throughout training.}
  \label{fig:modelloss}
\end{figure}

We also trained models where center frames (where the car was going 
straight) and curve frames (where the car was turning) were equally 
selected in each batch, and were pleasantly surprised at the change 
in the car's performance. With the second method, the car displayed a 
greater ability to stay in the center of the track (on the white 
tape). This was problematic, however, as the loss values changed with 
the training loss being 0.009 and the validation loss becoming 
0.0869, indicating that overfitting had become a problem. We believe, 
though, that this can be rectified through the collection of 
additional data for training and validation.

\begin{figure}[h]
  \centering
  \includegraphics[width=.55\textwidth]{figs/graph_run=.pdf}
  \caption{ Network visualization. }
  \label{fig:}
\end{figure}
\fixme{Is all of the network graph necessary or only certain parts?}
